---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## What's going on with this data?

Tracking my Instagram feed observations.

This dynamic report analyses the Instagram posts I observed over time using my Google Form. Each row in the dataset represents one post that I saw on my feed. I am using this report to explore what kinds of content appear most often, how long I spend viewing them, how I engage with them, and whether they seem targeted to me.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTrOzhX80p01vwQMLgBleh2LriokZe3IhZhxPI9qjzmHhhclMOOt-Fc679flI8mK3qlS90IAuSbVtxT/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    content_type = `What type of content is this post?`,
    time_seconds = `How many seconds did you spend viewing this post?`,
    engagement = `Did you engage with the post?`,
    related = `Relevance`,
    is_targeted = `Was this clearly targeted to you?`
  )

```

### Summary of the data

```{r}
summary_stats <- latest_data %>%
  summarise(
    total_observations = n(),
    mean_time_seconds = mean(time_seconds, na.rm = TRUE),
    max_time_seconds = max(time_seconds, na.rm = TRUE)
  )

top_content <- latest_data %>%
  count(content_type, sort = TRUE) %>%
  slice(1)

```

```{r}
summary_stats
top_content
```

I recorded **`r summary_stats$total_observations`** Instagram posts in total over the observation period.

The average time spent viewing each post was **`r round(summary_stats$mean_time_seconds, 1)` seconds**, indicating how long content typically holds my attention.

The maximum viewing time recorded was **`r summary_stats$max_time_seconds` seconds**, suggesting that some posts are significantly more engaging than others.

The most frequently observed content type was **`r top_content$content_type`**, appearing **`r top_content$n` times**, which suggests this type of content dominates my Instagram feed.


### Content type distribution

```{r}
plot1 <-latest_data %>%
  ggplot(aes(x = content_type)) +
  geom_bar() +
  labs(
    title = "Distribution of content types",
    x = "Content type",
    y = "Number of posts"
  ) +
  theme_minimal()

```  
```{r}
plot1
```

The bar chart above shows the distribution of content types observed on my Instagram feed.

It is clear that **`r top_content$content_type`** is the most common content type, which aligns with the summary statistics. This suggests that my feed is heavily influenced by this category of content.


### Engagement distribution

```{r}  
plot2<- latest_data %>%
  ggplot(aes(x = engagement)) +
  geom_bar() +
  labs(
    title = "Distribution of engagement types",
    x = "Engagement type",
    y = "Number of posts"
  ) +
  theme_minimal()

top_engagement <- latest_data %>%
  count(engagement, sort = TRUE) %>%
  slice(1)
```
```{r}
plot2
top_engagement
```
The bar chart above displays how I interacted with the posts I observed.

The most common engagement type was **`r top_engagement$engagement`**, indicating that this is the way I most frequently interact with content. This may suggest a preference for certain types of engagement over others.

